The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-07-27 paper.tex
improve the flux-scale figure so that plots aren't falling off the page

\begin{figure*}[p]
    \gridline{
        \fig{figures/flux-scale/flux-cyga}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-vira}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-hyaa}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-perb}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-lyna}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c48}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c147}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c286}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c295}{0.48\textwidth}{}
        \fig{figures/flux-scale/flux-3c353}{0.48\textwidth}{}
    }
    \gridline{
        \fig{figures/flux-scale/flux-3c380}{0.48\textwidth}{}
    }
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line), \citet{2012MNRAS.423L..30S}
        (dashed line), and \citet{1977A&A....61...99B} (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}

>>>>

\begin{figure*}[p]
    \includegraphics[width=\textwidth]{figures/flux-scale/flux-scale}
    \caption{
        This figure shows the measured fluxes (black points) of 11 sources plotted against the
        published spectra from \citet{2017ApJS..230....7P} (solid line above 50 MHz, dotted line
        below 50 MHz), \citet{2012MNRAS.423L..30S} (dashed line), and \citet{1977A&A....61...99B}
        (dot-dash line).
    }
    \label{fig:flux-scale}
\end{figure*}
